Study 1

### 2022-02-05 code/analysis.Rmd
start text analysis

 - get empirica time recording to behave (grumble)
 - read feedback
 - remove incomplete game(s)

@@

@@

d.round_results.raw <- read_csv(here(data_location,'rounds.csv'),guess_max=10000) %>% 
  filter(createdAt >= date_start) %>% 
  rename_with(~ gsub("data.", "", .x, fixed = TRUE)) %>% 
  rename_with ( ~ gsub("room", "player", .x, fixed=T)) %>% 
    rename_with ( ~ gsub("player", "player_", .x, fixed=T)) %>% 
    rename_with ( ~ gsub("response", "_response", .x, fixed=T)) %>% 
  rename_with( ~ gsub("time", "_time", .x, fixed=T)) %>% 
  select(-chat) %>% 
  gather(key, value, starts_with('player')) %>% 
  separate(key, into = c('blah', 'playerId', 'info')) %>% 
  spread(info, value) %>% 
  select(-blah) %>% 
  select(-stageIds,-index,-createdAt,-submitted) %>% 
  filter(!is.na(response)) %>% 
  mutate(time=as.numeric(time)/1000) %>% 
  mutate(targets=map(targets, .f=ParseJSONColumn)) %>% 
  unnest(targets) %>% 
  mutate(image = gsub('/experiment/', '', image, fixed=TRUE),
        image = gsub('.jpeg', '', image, fixed=TRUE)) %>% 
  pivot_wider(names_from=label, names_prefix="box_", values_from=image) %>% 
    mutate(payoffs=map(payoffs, .f=ParseJSONColumn)) %>%
  unnest(payoffs) %>% 
  mutate(AA=ifelse(role=="p1", AA.p1, AA.p2),
         AB=ifelse(role=="p1", AB.p1, AB.p2),
         BA=ifelse(role=="p1", BA.p1, BA.p2),
         BB=ifelse(role=="p1", BB.p1, BB.p2)) %>% 
  left_join(d.games) %>% 
  write_csv(here(data_location, 'raw_results.csv'))

d.exit.survey <- read_csv(here(data_location, 'player-inputs.csv')) %>%
  filter(createdAt >= date_start) %>%
  left_join(d.games, by = c('gameId')) %>%
    rename_with(~ gsub("data.", "", .x, fixed = TRUE)) %>% 
  write_csv(here(data_location,'exit.csv'))

@@

summary <- d.round_results %>% group_by(repNum, gameId, game_cond, chat_cond) %>% 
  filter(time<181) %>% 
  summarize(max_time=max(time)) %>% 
  group_by(gameId, game_cond, chat_cond) %>% 
  summarize(total_time=sum(max_time)/60,
            num_rounds=max(repNum)) %>% 
  filter(num_rounds==39)

@@

ggplot(chat, aes(x=str_c(game_cond," ", chat_cond), y=words))+geom_jitter(width=.1)+
  labs(title="Words produced in pre-chat", y="words", x="condition")
```
People talked some. I haven't looked at the transcripts at all.

@@

ggplot(is_chat, aes(x=repNum, y=pct_chat, color=game_cond))+geom_point()+
  labs(title="Pct games who said anything", y="pct")
```
Currently open questions -- is that game-related chat, or is it just that it's a friendlier game? 
Does the chatting help?

# Does chat help?

@@

```
Looks like chatting helps for BoS, doesn't get used much for PD.

@@

>>>>

 - get empirica time recording to behave (grumble)
 - read feedback

@@

## Pre-reg
According to https://osf.io/8fnze, the analyses I'm going to do:

This is exploratory research, here are some things we plan to explore. 
role of language on score. For each type of game, do games with language have higher overall scores ? Is this related to if language was actually used? 
Quantity and type of language over rounds. How much language is produced each round in PD v BoS? Does it decline in later rounds? 
What type of language is used? Is it just identifying what to select or is there meta-strategy/negotiation?
Are pairs converging to predictable strategies?

@@

d.round_results.raw <- read_csv(here(data_location,'rounds.csv'),guess_max=10000) %>% 
  filter(createdAt >= date_start) %>% 
  rename_with(~ gsub("data.", "", .x, fixed = TRUE)) %>% 
  rename_with ( ~ gsub("room", "player", .x, fixed=T)) %>% 
    rename_with ( ~ gsub("player", "player_", .x, fixed=T)) %>% 
    rename_with ( ~ gsub("response", "_response", .x, fixed=T)) %>% 
  rename_with( ~ gsub("time", "_time", .x, fixed=T)) %>% 
  select(-chat) %>% 
  gather(key, value, starts_with('player')) %>% 
  separate(key, into = c('blah', 'playerId', 'info')) %>% 
  spread(info, value) %>% 
  select(-blah) %>% 
  select(-stageIds,-index,-createdAt,-submitted) %>% 
  filter(!is.na(response)) %>% 
  mutate(time=as.numeric(time)/1000) %>% 
  mutate(targets=map(targets, .f=ParseJSONColumn)) %>% 
  unnest(targets) %>% 
  mutate(image = gsub('/experiment/', '', image, fixed=TRUE),
        image = gsub('.jpeg', '', image, fixed=TRUE)) %>% 
  pivot_wider(names_from=label, names_prefix="box_", values_from=image) %>% 
    mutate(payoffs=map(payoffs, .f=ParseJSONColumn)) %>%
  unnest(payoffs) %>% 
  mutate(AA=ifelse(role=="p1", AA.p1, AA.p2),
         AB=ifelse(role=="p1", AB.p1, AB.p2),
         BA=ifelse(role=="p1", BA.p1, BA.p2),
         BB=ifelse(role=="p1", BB.p1, BB.p2)) %>% 
  left_join(d.games)

d.exit.survey <- read_csv(here(data_location, 'player-inputs.csv')) %>%
  filter(createdAt >= date_start) %>%
  left_join(d.games, by = c('gameId')) %>%
    rename_with(~ gsub("data.", "", .x, fixed = TRUE))

d.complete <- d.round_results.raw %>% group_by(gameId, playerId) %>% 
  summarize(max_rep=max(repNum)) %>% filter(max_rep==39) %>% select(gameId,playerId) %>% 
  write_csv(here(data_location,"complete.csv"))

#remove that one game that didn't complete
d.chat <- d.chat.raw %>% inner_join(d.complete) %>% 
  write_csv(here(data_location, 'raw_chat.csv'))
d.round_results <- d.round_results.raw %>% inner_join(d.complete) %>% 
  write_csv(here(data_location, 'raw_results.csv'))
d.exit <- d.exit.survey %>% inner_join(d.complete) %>% 
  write_csv(here(data_location,'exit.csv'))

@@

summary <- d.round_results %>% group_by(repNum, gameId, game_cond, chat_cond) %>% 
  filter(time<181) %>% 
  summarize(max_time=max(time)) %>% 
  group_by(gameId, game_cond, chat_cond) %>% 
  summarize(total_time=sum(max_time)/60,
            num_rounds=max(repNum))

@@

ggplot(chat, aes(x=str_c(game_cond," ", chat_cond), y=words))+geom_jitter(width=.1)+
  labs(title="Words produced in pre-chat", y="words", x="condition")
```

People talked some. I haven't looked at the transcripts at all.

@@

ggplot(is_chat, aes(x=repNum, y=pct_chat, color=game_cond))+geom_point()+
  labs(title="Pct games who said anything", y="pct")
```

Currently open questions -- is that game-related chat, or is it just that it's a friendlier game? 
Does the chatting help?

## What are people saying?

```{r}
library(qdap)

game_chat %>% ungroup() %>%  summarize(s=sum(words)) #2093 total words

chat <-  read_csv(here(data_location, "raw_chat.csv")) %>%
  filter(!is.na(targets)) %>% 
  filter(chat_cond=="chat") %>% 
  filter(!is.na(text)) %>% 
  select(gameId,game_cond,repNum, text) %>% 
  mutate(text=strip(text)) %>% 
  mutate(length=str_count(text, "\\w+")) %>% 
  filter(length>0)

ggplot(chat, aes(length))+geom_bar()

Most utterances are single word utterances, we'll consider these and multi word utterances separately.

```{r}
#single world
words <- chat %>% filter(length==1) %>% pull(text) %>% word_list() %>% pull(fwl)

head(words$all, 20)
#chat %>% filter(length==1) %>% nrow()
colors <- c("green", "blue", "pink","purple", "yellow", "red", "orange", "brown", "grey","white", "salmon", "gray")

chat %>% filter(length==1) %>% filter(text %in% colors) %>% nrow()
```

There are 743 singletons. Of these 100 are ok/okay, at least 433 are color words, more once you count rarities and misspellings. There's also a bunch of singleton letters -- these seem to be single letter color abbreviations?

From skimming transcripts, looks like multi's occur earlier in general. But we're confounded by pleasantries at random times (talking about where they live, etc).

chat %>% mutate(singleton=ifelse(length==1, "single", "multi")) %>% ggplot(aes(repNum, fill=singleton))+geom_bar()+facet_grid(singleton~game_cond)

```{r}
chat %>% filter(length>1) %>% select(game_cond, repNum, text) %>% head(40) %>% knitr::kable()

```
# Does chat help?

@@

Looks like chatting helps for BoS, doesn't get used much for PD.

@@

# Is the other player a human?

```{r bot}

bot <- read_csv(here(data_location, "exit.csv")) %>% 
  filter(!is.na(game_cond) & !is.na(chat_cond)) %>% 
  group_by(game_cond, chat_cond, human) %>% 
  tally() %>% 
  pivot_wider(names_from=human, values_from=n)

bot
```

Only 10-20% of players think the other person is a bot!
